---
title: "Lab1"
author: "Hyeonjoon David Park"
date: "`r Sys.Date()`"
output: 
    html_document: rmarkdown::html_vignette
    df_print: paged
    highlights: pygments
    theme: spacelab
    toc: yes
    toc_float: yes
vignette: >
  %\VignetteIndexEntry{Lab1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette brielfy introduces basic story about R package making, required formulas, and applied examples.

```{r setup}
library(Lab1Intro)
```

# Links about package making in R

## Useful links that leads to documentation about package making

1. Hadley Wickham and Jennifer Bryan, R Packages, O'Reilly
<https://r-pkgs.org/>[link](https://r-pkgs.org/)

2. Relevant Youtube videoclip
<https://www.youtube.com/watch?v=79s3z0gIuFU>[link](https://www.youtube.com/watch?v=79s3z0gIuFU)

3. R Studio support page for R package making

<https://support.rstudio.com/hc/en-us/articles/200486498-Package-Development-Prerequisites>[link](https://support.rstudio.com/hc/en-us/articles/200486498-Package-Development-Prerequisites)


## Github repository address

The following is the link for my githup repository address.

<https://github.com/david92231/MATH5793.git>[link](https://github.com/david92231/MATH5793.git)


# LaTeX formulae

## a. JW(1-1,4,5) pages 7,8

Sample mean

$$ \bar{x}_{k} = \frac{1}{n}\sum^{n}_{j=1}x_{jk} \qquad k = 1, 2, \dots, p  $$

Sample covariance

$$ s_{ik} = \frac{1}{n}\sum^{n}_{j=1}(x_{ji}-\bar{x}_{i})(x_{jk}-\bar{x}_{k}) \qquad i = 1,2,\dots,p, \quad k = 1,2,\dots,p $$

Sample correlation coefficient

$$ \begin{equation*}
      \begin{aligned}
        r_{ik} &= \frac{s_{ik}}{\sqrt{s_{ii}}\sqrt{s_{kk}}}\\
               &\\
               &= \frac{\sum^{n}_{j=1}(x_{ji}-\bar{x}_{i})(x_{jk}-\bar{x}_{k})}{\sqrt{\sum^{n}_{j=1}(x_{ji}-\bar{x}_{i})^{2}}\sqrt{\sum^{n}_{j=1}(x_{jk}-\bar{x}_{k})^{2}}}\\
               &\\
               & \text{for all} \quad i = 1,2,\dots,p \quad \text{and} \quad k = 1,2,\dots,p
			\end{aligned}
\end{equation*} $$


## b. JW(3-27) page 139

$$ \begin{equation*}
      \begin{aligned}
        \mathbf{\bar{x}} &= \frac{1}{n}\mathbf{X}'\mathbf{1}\\
        \mathbf{s} &= \frac{1}{n-1}\mathbf{X}'\bigg(\mathbf{I}-\frac{1}{n}\mathbf{11}' \bigg)\mathbf{X}
      \end{aligned}
\end{equation*} $$

## c & d. JW(3-28,29)

$$ \begin{equation*}
      \begin{aligned}
        \mathbf{D}_{p \times p}^{1/2} &= \left[ \begin{array}{cccc}
                  \sqrt{s_{11}} & 0 & \cdots & 0\\
                  0 & \sqrt{s_{22}} & \cdots & 0\\
                  \vdots & \vdots & \ddots & \vdots\\
                  0 & 0 & \cdots & \sqrt{s_{pp}}
                  \end{array}\right]\\
                  &\\
                  \text{Then}
                  &\\
                  &\\
        \mathbf{D}_{p \times p}^{-1/2} &= \left[ \begin{array}{cccc}
                  \frac{1}{\sqrt{s_{11}}} & 0 & \cdots & 0\\
                  0 & \frac{1}{\sqrt{s_{22}}} & \cdots & 0\\
                  \vdots & \vdots & \ddots & \vdots\\
                  0 & 0 & \cdots & \frac{1}{\sqrt{s_{pp}}}
                  \end{array}\right]\\
                  &\\
                  \text{Since}
                  &\\
                  &\\
          \mathbf{S} &= \left[ \begin{array}{cccc}
                  s_{11} & s_{12} & \cdots & s_{1p}\\
                  \vdots & \vdots & \ddots & \vdots\\
                  s_{1p} & s_{2p} & \cdots & s_{pp}
                  \end{array}\right]\\
                  &\\
                  \text{and}
                  &\\
                  &\\
          \mathbf{R} &= \left[ \begin{array}{cccc}
                  \frac{s_{11}}{\sqrt{s_{11}}\sqrt{s_{11}}} & \frac{s_{12}}{\sqrt{s_{11}}\sqrt{s_{22}}} & \cdots & \frac{s_{1p}}{\sqrt{s_{11}}\sqrt{s_{pp}}}\\
                  \vdots & \vdots & \ddots & \vdots\\
                  \frac{s_{1p}}{\sqrt{s_{11}}\sqrt{s_{pp}}} & \frac{s_{2p}}{\sqrt{s_{22}}\sqrt{s_{pp}}} & \cdots & \frac{s_{pp}}{\sqrt{s_{pp}}\sqrt{s_{pp}}}\\
                  \end{array}\right]\\
                  &\\
                  &= \left[ \begin{array}{cccc}
                  1 & r_{12} & \cdots & r_{1p}\\
                  \vdots & \vdots & \ddots & \vdots\\
                  r_{1p} & r_{2p} & \cdots & 1
                  \end{array}\right]\\
                  &\\
                  \text{we have}
                  &\\
                  &\\
          \mathbf{R} &= \mathbf{D}^{-1/2}\mathbf{S}\mathbf{D}^{-1/2}
      \end{aligned}
\end{equation*} $$


# Example using the data in Table 1.2 JW page 15

## a. The sample mean

```{r example1}
# Load the data

dat = read.delim("T1-2.dat", header = F, sep="")
head(dat)

# Run the mean vector function
meanvector(dat)
```

## b. Sample covariance(biased)

```{r example2}
# Run the sample covariance matrix function
covmat(dat)
```

## c. Sample correlation

```{r example3}
# Run the sample correlation matrix function
corrmat(dat)
```

# Grades for this class

$$
\begin{array}{|c|c|}\hline
Group & Weight \\\hline
\text{Clicker Quizzes} & 10\% \\
Assignments & 20\% \\
Laboratories & 10\%\\
Mid-term1 & 10\%\\
Mid-term2 & 10\%\\
Final & 30\%\\
Projects & 10\%\\\hline
\end{array}
$$




